MSstatsPTM: Statistical relative quantification of post-translational modifications in bottom-up mass spectrometry-based proteomics

### 2022-07-11 main/MSstatsPTM_Main.tex
Suggestion for Fig 3 caption

\begin{figure}[ht]
\centering
\includegraphics[scale=.8]{images/MSstatsPTM_design.png}
\caption{The $MSstatsPTM$ workflow. The names of the R functions used for each step are highlighted in red. The package's workflow starts after modified and unmodified peptide quantification. First tool specific pre-processing is performed, this includes modification site identification, general data cleaning, and formatting the data into the format needed for the package. The next step is feature level summarization, which summarizes features up to the modification level for the PTM data, and the protein level for the protein data. In the final step a model is fit to identify differential PTMs and unmodified proteins across conditions and the PTM model is adjusted for changes in the unmodified protein. After both the summarization and group comparison steps, plots can be created to summarize the results.}
\label{fig:msstatsptm_design}
\end{figure}

>>>>

\begin{figure}[ht]
\centering
\includegraphics[scale=.8]{images/MSstatsPTM_design.png}
\caption{The $MSstatsPTM$ workflow. The names of the R functions used for each step are highlighted in red. \todo{In the caption, could you try the following order: applicable to experimental designs XXX; takes as input XXX; separate parallel analyses for global proteome and PTM. (No need to read off the figure, just clarify the content)} \todo{Would it be possible to modify the figure to reflect the parallel nature of the processing/analyses?} The package's workflow starts after modified and unmodified peptide quantification. First tool specific pre-processing is performed, this includes modification site identification, general data cleaning, and formatting the data into the format needed for the package. The next step is feature level summarization, which summarizes features up to the modification level for the PTM data, and the protein level for the protein data. In the final step a model is fit to identify differential PTMs and unmodified proteins across conditions and the PTM model is adjusted for changes in the unmodified protein. After both the summarization and group comparison steps, plots can be created to summarize the results.}
\label{fig:msstatsptm_design}
\end{figure}
